Quantifying unmet ICU beds in tertiary hospitals in urban India using Prospective Score Matching 

### 2022-09-20 manuscript.Rmd
20 sep kväll

NOTE2SELF: för projektredogörelsen feta ut och ha med paragraferna här som temporaries och säg till när de är klara för kommentering intro och metoddelen, 
Fråga Johanna: 3-5 sidor ja men det är en rekommendation och formatet med omfattande bakgrund passar inte den här typen av studie. jag kan men jag vet inte om det är meningsfullt att producera 2 sidor text baraföratt? I instruktionen skriver KI själva att det är en kontrollmekanism bara "koordinatorn får en uppfattning om progress i projektet,". Kan jag bara motivera utformningen så är jag inte orolig jag la frågan till kursadmin
<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->

@@

Trauma disproportionately affects young, otherwise healthy individuals. They are often the primary breadwinners for their families and therefore the detrimental impact of trauma go beyond mortality or substantial loss of disease-free years of life for the affected individuals, it also carries a considerable financial and social harm on their family members and communities. @traumaLMIC

@@

The theory being examined in this masters thesis is that there exist subset of the TITCO-I dataset that didn't go to the ICU, but are very similar to the patients that did go to the ICU, in the covariates that caused ICU-treated patients to receive this intervention. The thesis is that these patients were not admitted to the IC for lack of such resources. These patients will be identified using propensity score matching.

@@

It is important to note that all patients have sequence numbers that corresponded to the chronological order in which they arrived at any of the participating hospitals, and that sequence number has been kept intact. Keeping this sequence number variable intact allows for many useful operations such as examinations of trends in the data, while it is not possible to undo the date randomization by the sequence number variable, such an equation system is still underdetermined. Unfortunately this means it is also not possible to reconstruct the patient volumes at any given hospital on any given day and from that rate of resource engagement. In addition, 47 patient data were randomly deleted to prevent identification via the sequence number variable.

>>>>

NOTE2SELF: för projektredogörelsen feta ut och ha med paragraferna här som temporaries och säg till när de är klara för kommentering intro och metoddelen, 
Fråga Johanna: 3-5 sidor ja men det är en rekommendation och formatet med omfattande bakgrund passar inte den här typen av studie och det blir ganska tydligt vad du menar med det när jag försöker producera texten. Mina kurskamraters projekt handlar om specifika sjukdomar eller medicinska interventioner eller liknande och då är det naturligt och viktigt att beskriva dem utförligt, men jag har inte riktigt något motsvarande min punchline är just i metoddelen.  Jag skulle kunna skriva ännu mer om indisk traumastatistik, hur dåligt det är med trauma, recycla resonemanget om hur bl.a. motorcykelolyckor har olika karakteristik i Indien vs nordamerika men jag vet inte om det är meningsfullt att producera 2 sidor text baraföratt. 
I instruktionen skriver KI själva att det är en kontrollmekanism bara "koordinatorn får en uppfattning om progress i projektet,". Kan jag bara motivera utformningen så är jag inte orolig jag la frågan till kursadmin
<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->

@@

Trauma is a main cause of mortality and morbidity to otherwise healthy and young individuals, and dispropotionately affect this demographic. People in this demographic are also oftentimes the primary or sole breadwinners for their families. Therefore the detrimental impact of trauma go beyond mortality or substantial loss of disease-free years of life for the affected individuals, it also carries a considerable financial and social harm on their family members and communities. @traumaLMIC

@@

The theory being examined in this masters thesis is that there exist subset of the TITCO-I dataset that didn't go to the ICU, but are very similar to the patients that did go to the ICU, in the covariates that caused ICU-treated patients to receive this intervention. The thesis is that these patients were not admitted to the ICU only for lack of such resources, not by a medical assessment. In statistics, such a group would be akin to an non-experimental conrol group, and these patients will be identified using propensity score matching.

@@

It is important to note that all patients have sequence numbers that corresponded to the chronological order in which they arrived at any of the participating hospitals, and that sequence number has been kept intact. Keeping this sequence number variable intact allows for many useful operations such as examinations of trends in the data, while it is not possible to undo the date randomization by the sequence number variable, such an equation system is still underdetermined. Unfortunately this means it is also not possible to reconstruct the patient volumes at any given hospital on any given day and from that rate of resource engagement. Nor is it possible to distinguish if patients who were made to wait for their first assessment were so because their injuries were deemed as less severe or if it was because health care staff was overwhelmed which is an important distinction.

In addition, 47 patient data were randomly deleted to prevent identification via the sequence number variable.
